### 2019-01-01 index.Rmd
clarify github master branch language

## Bug Fixes in v0.1.3
The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed in the current GitHub release:

>>>>

## Bug Fixes in v0.1.3
The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed on the current GitHub master branch:
